Multi-resolution Neural Field Estimation

### 2011-03-06 Multiresolution_framework/ltx/manuscript.tex
edit to abstract
defined FEM in the introduction

\begin{abstract}
%\boldmath
The Integro-difference equation (IDE) is an increasingly popular model of spatio-temporal processes. Here we develop a multiresolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets. State and parameter estimation is performed using the Expectation Maximisation (EM) algorithm.
\end{abstract}
% Note that keywords are not normally used for peerreview papers.
% \begin{IEEEkeywords}
% Neural field model, multiresolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
% \end{IEEEkeywords}
% \IEEEpeerreviewmaketitle
\section{Introduction}
\IEEEPARstart{T}{he} human brain \mike{cortex?} has a multiresolution architecture, where spatial scales for information processing and transfer range from individual proteins in synapses\cut{, to neurons,} to networks of neurons. This multiresolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics. This paper introduces a multiresolution data-driven framework for neural field modeling, the MultiResolution Approximate Integro-Difference Equation (MRAIDE), to address this challenge.

@@

The first work describing data-driven mesoscopic neural modeling~\cite{Valdes1999} used a neural mass model~\cite{LopesDaSilva1976,Zetterberg1978} to fit EEG data. This approach was extended to coupled neural masses \cut{(using another model~}\cite{Jansen1995}) through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\cite{David2003}. Following this work, data-driven modeling was extended to continuum field equations that explain the richer dynamics of spatiotemporal neural fields \cite{Galka2008,schiff2008kalman,Daunizeau2009}. Most recently a framework was developed where a finite element model of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}. The current paper is an extension to this recent study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex. In this way, a flexible framework is created where both macroscopic and microscopic behaviour of the system can be represented simultaneously.

>>>>

\begin{abstract}
%\boldmath
The Integro-difference equation (IDE) is an increasingly popular model of spatio-temporal processes. Here we develop a multiresolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets. State and parameter estimation is performed using the Expectation Maximisation (EM) algorithm. A synthetic example is given
to demonstrate the framework.
\end{abstract}
% Note that keywords are not normally used for peerreview papers.
% \begin{IEEEkeywords}
% Neural field model, multiresolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
% \end{IEEEkeywords}
% \IEEEpeerreviewmaketitle
\section{Introduction}
\IEEEPARstart{T}{he} human brain \mike{cortex?} has a multiresolution architecture, where spatial scales for information processing and transfer range from individual proteins in synapses\cut{, to neurons,} to networks of neurons. This multiresolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics. This paper introduces a multiresolution data-driven framework for neural field modeling, the MultiResolution Approximate Integro-Difference Equation (MRAIDE), to address this challenge.

@@

The first work describing data-driven mesoscopic neural modeling~\cite{Valdes1999} used a neural mass model~\cite{LopesDaSilva1976,Zetterberg1978} to fit EEG data. This approach was extended to coupled neural masses \cut{(using another model~}\cite{Jansen1995}) through a Bayesian estimation scheme dubbed Dynamic Causal Modeling (DCM)~\cite{David2003}. Following this work, data-driven modeling was extended to continuum field equations that explain the richer dynamics of spatiotemporal neural fields \cite{Galka2008,schiff2008kalman,Daunizeau2009}. Most recently a framework was developed where a finite element model \parham{(FEM)} of the neural field (via a global Galerkin projection) was formed, using a basis function decomposition, to transform the PDE neural field equations into a finite dimension system to facilitate efficient state and parameter estimation~\cite{Freestone2011}. The current paper is an extension to this recent study, where we derive a neural field state-space model that accounts for the multi-resolution architecture and spatial dynamics of the human cortex. In this way, a flexible framework is created where both macroscopic and microscopic behaviour of the system can be represented simultaneously.
